Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-13 paper.tex
NMRShiftDB is not public domain; it's GNU FDL
Added a practical use case of three BO products: Oscar[3], Bioclipse, and NMRShiftDB.org
Remove early refs to BO projects.

Many of the current operations in installing and running chemical
computations and using the data are integration and customisation
rather than fundamental algorithms. It is very difficult to create
universal platforms that can be distributed and run by a wide range of
different users, and in general, the Blue Obelisk deliberately does
not address these. Our approach is to produce components that can be
embedded in many environments, from stand-alone applications to web
applications, databases and workflows.
We believe that a chemical laboratory with reasonable access to common
software engineering techniques should be able to build customised applications
using Blue Obelisk components and standard infrastructure such as
workflows (KNIME or Taverna) and databases (MySQL, CouchDB etc.).
Where the Blue Obelisk itself produces data resources (NMRShiftDB,
CrystalEye, Quixote etc.) they are normally done with Open components
so that the community can, if necessary, replicate them.

@@

  \subsection*{Table 2 - Open Data in chemistry.}
    Overview of major open chemical data available under a license or waiver
    compatible with the Panton Principles.
    \par \mbox{}
    \par
    \mbox{
\begin{tabular}{|l|c|l|}
  %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
  \hline \textbf{Name} & \textbf{License/Waiver} & \textbf{Description} \\ \hline
  \textbf{ChemPedia} & CC0 & Crowd-sourced chemical names (project discontinued) \\ \hline
  \textbf{CrystalEye}     & PPDL & Crystal structures from primary literature \\ \hline
  \textbf{NMRShiftDB} & Public Domain & Database of NMR spectra of organic compounds \\ \hline
  \textbf{ONS Solubility} & CC0 & Solubility data for various solvents \\ \hline
  \textbf{Reaction Attempts} & CC0 & Data on successful and unsuccessful reactions \\ \hline
\end{tabular}
      }

>>>>

Many of the current operations in installing and running chemical
computations and using the data are integration and customisation
rather than fundamental algorithms. It is very difficult to create
universal platforms that can be distributed and run by a wide range of
different users, and in general, the Blue Obelisk deliberately does
not address these. Our approach is to produce components that can be
embedded in many environments, from stand-alone applications to web
applications, databases and workflows.
We believe that a chemical laboratory with reasonable access to common
software engineering techniques should be able to build customised applications
using Blue Obelisk components and standard infrastructure such as
workflows and databases.
Where the Blue Obelisk itself produces data resources
they are normally done with Open components
so that the community can, if necessary, replicate them.

@@

  \subsection*{Table 2 - Open Data in chemistry.}
    Overview of major open chemical data available under a license or waiver
    compatible with the Panton Principles.
    \par \mbox{}
    \par
    \mbox{
\begin{tabular}{|l|c|l|}
  %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
  \hline \textbf{Name} & \textbf{License/Waiver} & \textbf{Description} \\ \hline
  \textbf{ChemPedia} & CC0 & Crowd-sourced chemical names (project discontinued) \\ \hline
  \textbf{CrystalEye}     & PPDL & Crystal structures from primary literature \\ \hline
  \textbf{ONS Solubility} & CC0 & Solubility data for various solvents \\ \hline
  \textbf{Reaction Attempts} & CC0 & Data on successful and unsuccessful reactions \\ \hline
\end{tabular}
      }
